---
title: "03/08/2020"
author: "RUCHIKA LALLA 2048130"
date: "8/3/2020"
output: word_document
---

```{r setup, cache=F}
knitr::opts_chunk$set(error = TRUE)
```

# EXAMPLES OF BASIC R CONCEPTS

```{r}
#Mathematical, Logical, Assign Values
3+2
6*7
```
Here, we revise the use of mathematical operators to use R as a calculator.

```{r}
#Logical Values
3<4
2+2==5
```

T and F are shorthand for TRUE and FALSE.
Logical operators can help check a certain condition.

```{r}
Happy Learning
```
Since the string was not enclosed in quotes, it cannot be printed or stored as a string.

```{r}
"Happy Learning"
```

Now that the string was enclosed in quotes, it can be printed or assigned to a variable.

```{r}
x<-42
x/7
```

Here, since R has stored data of the numeric class in the variable x, mathematical operations can be carried out on it as well.

```{r}
x<-"Happy Learning"
x/7
```

However, R reassigns the variable if some other data is attached to the variable name. Now, a string is attached to x. Thus, no mathematical operation can be carried out on it.

```{r}
x
```

The variable can also be printed.

```{r}
#Functions
sum(2,3,5)
c=rep("576",times=3)
c
rep("Happy Learning",times=3)
sqrt(64)
```

Functions can be used to carry out a variety of operations. These operations can be mathematical, logical or can even be used to generate random numbers/lists.

```{r}
c/8
```

Since we generated a list of numbers in quotes, they act as strings. Thus, no mathematical operations can be carried out on strings.

```{r}
#Vector with String
c('a','b','c') #c is short for combine
```

Vector is simply a list of values. It can be of any data type class.

```{r}
#Vector with Numeric
c(3,6,7)
```

```{r}
a=(5,6,7)
a
```

Here, the vector was not created because we did not use the combine command. We cannot create vectors without this command.

```{r}
#Sequence Vector
5:9
seq(5,9)#increment of 1 is the default option
seq(5,9,0.5)
9:5 #vector from 9 down to 5
```

The sequence vector is necessary for generating a sequence required for any calculation.

```{r}
#Vector Access
sentence<-c('you','me','R')
sentence[3]
sentence[1]
```

The benefit of using vectors in R is that we can access different items, change items in the list, remove items or even add items.

```{r}
#Change and Add in a Vector
sentence[3]<-'SAS'
sentence[4]<-'SPSS'
sentence
sentence[c(1,3)] #access 1st and 3rd element
sentence[2:4] #access 2nd to 4th element
```

```{r}
#Vector Math
a<-c(4,5,6)
a
a+1
a/2
a*2
```

Basic mathematical operations can be carried out on vectors.

```{r}
#Vector Addition and Multiplication
b<-c(7,8,9)
a+b
a-b
a*b
sqrt(a)
```

In addition, two matrices can also be operated upon.

```{r}
#Vector:Compare Items
a==c(4,100,6)
```

You can also check if some items exist in the list using logical operations.

```{r}
#NA Value
a<-c(1,3,NA,7,9)
sum(a)
```

When an NA value is included in a vector or appears when division is carried out and the denominator does not exist, it can hamper other operations that you would want to carry out.

```{r}
help(sum)
```
```{r}
sum(a,na.rm=TRUE) #the rm command removes NA
```

Using the na.rm command, we can remove the NA values and carry out the required operations.

```{r}
#Matrices
matrix(0,3,4)
```

This is a very simple way to create a zero matrix.

```{r}
#Vector to Matrix
a<-1:12
print(a)
matrix(a,3,4)
```

Using a vector, we can generate the required matrix.