---
title: "08_08_20"
author: "RUCHIKA LALLA 2048130"
date: "8/8/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# MATRICES

## Creating a 3x4 matrix with all fields '0'
```{r}
matrix(0,3,4)
```

Thus, a 3x4 zero matrix has been created.

## Using a vector to initiate a matrix
```{r}
a<-1:12   #vector has been created to design a 3x4 matrix
a
```

```{r}
matrix(a,3,4)
```

Thus, a 3x4 matrix has been created.

## Dim command for matrix
```{r}
sijo<-1:8  #created a 8 item vector
dim(sijo)<-c(2,4)  #dimensions have been added to the vector
print(sijo)
```

Here, the matrix is created from a vector by assigning dimensions to it.

## Matrix Access
```{r}
sijo[2,]  #see the 2nd row in the matrix
```

```{r}
sijo[,4]   #see the 4th column in the matrix
```

```{r}
sijo[2,4]  #see intersection of 2nd rown and 4th column
```

```{r}
sijo[,2:4]   #see column 2 to 4 in the matrix
```

```{r}
a<-sijo[,2:4]  #create and print a subset of the matrix
a
```

Thus, matrix access has been carried out using simple commands.

## Practice Questions

### Question 1
Consider A=matrix(c(2,0,1,3), ncol=2) and B=matrix(c(5,2,4,-1), ncol=2).
a) Find A + B
b) Find A – B

```{r}
A=matrix(c(2,0,1,3),ncol=2)
B=matrix(c(5,2,4,-1),ncol=2)
A
B
```

```{r}
A+B
A-B
```


### Question 2
Find aA, where a=3.

```{r}
3*A
```

### Question 3
Using the the diag function build a diagonal matrix of size 4 with the following values in the diagonal 4,1,2,3.

```{r}
diag(c(4,1,2,3),nrow=4,ncol=4)
```

### Question 4
Find the solution for Ab, where A is the same as in the previous question and b=c(7,4).

```{r}
b=c(7,4)
A*b
```

### Question 5
Find the solution for AB, where B is the same as in question 1.

```{r}
A*B   #only multiplies each corresponding element
```

```{r}
crossprod(A,B)  #calculates the cross product
```

### Question 6
Find the transpose matrix of A.

```{r}
t(A)
```

### Question 7
Find the inverse matrix of A.

```{r}
library(matlib)
```

```{r}
inv(A)
```


### Question 8
```{r}
solve(A,b)
```

### Question 9
Using the function eigen find the eigenvalue for A.

```{r}
eigen(A)
```

### Question 10
Find the eigenvalues and eigenvectors of A’A . Hint: Use crossprod to compute A’A.

```{r}
A_=t(A)
A_A=crossprod(A_,A)
eigen(A_A)
```

## CONCLUSION
Thus, exploring further matrix functions, we are able to carry out multiple different matrix operations.