---
title: "Assignment1_2048130"
author: "RUCHIKA LALLA 2048130"
date: "8/8/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# ASSIGNMENT 1

In this assignment, we attempt to solve ten questions based on the concepts completed in the previous classes.

## Question 1

Add 3 to 7, multiply 4 and 8.

```{r}
3+7
4*8
```

Using R as a calculator, we are able to carry out the specified operations.

## Question 2

Test logical statements 12 >18 and 12+18 = 40

```{r}
12>18
12+18==40
```

Thus, R reported both of the logical statments as FALSE as they are not valid.

## Question 3

Type I HAVE LEARNT R 3 times.

```{r}
a="I HAVE LEARNT R"
b=c(a,a,a)
print(b)
```

Using a vector, we are able to print the required statement three times.

## Question 4

Create a vector name dear having 3 items Bangalore, Kolkata, Mumbai.

```{r}
dear=c("Bangalore","Kolkata","Mumbai")
dear
```

The required vector is created, and has been printed for cross-reference.

## Question 5

Create a vector name dearer having 3 items 84, 65, 39.

```{r}
dearer=c(84,65,39)
dearer
```

The required vector is created, and has been printed for cross-reference.

## Question 6

Create a vector name dearest having numbers from 101 to 107.

```{r}
dearest=c(101:107)
dearest
```

The required vector is created, and has been printed for cross-reference.

## Question 7

Access the third item in vector dear.

```{r}
dear[3]
```

Thus, we are able to access the third item in the vector dear.

## Question 8

Add new city, Chennai at 4 th place in vector dear.

```{r}
dear[4]<-"Chennai"
dear
```

The 4th city Chennai has been added to the vector dear, which is verified by printing the vector.

## Question 9

Access 2 nd & 4 th item in vector dear.

```{r}
dear[2]
dear[4]
```

Thus, we are able to access the 2nd and 4th element in the vector dear.

## Question 10

Create a vector name d having numbers 4, 5, 6 and another vector h having numbers 2, 3, 4. Multiply vector d with h.

```{r}
d=c(4,5,6)
h=c(2,3,4)
d*h
```

Using simple arithmetic operations on vectors, we are able to carry out the required operation.

# CONCLUSION

Thus, using the concepts of vectors and basic R functions, we are able to solve the given ten questions.