---
title: "11-08-20"
author: "RUCHIKA LALLA 2048130"
date: "8/11/2020"
output: word_document
---

```{r setup, cache=F}
knitr::opts_chunk$set(error = TRUE)
```

# FUNCTIONS AND LOOPS

# FUNCTIONS

Functions can be defined with any number of named arguments. The arguments specify the components to be used in the function. Arguments can be of any type (eg- vectors, data frames, lists, etc.)

Syntax: Name<-function(argument) {statement}

```{r}
Myfirstfn<-function(x){x+x}
Myfirstfn(10)
Myfirstfn(15)
```

```{r}
MyFirstfn(11)
```

```{r}
Mysecondfn<-function(t,z) { #code is case-sensitive
  value=z*3
  value=value*t
  print(value)
}
```

```{r}
Mysecondfn<-function(t,z) { #code is case-sensitive
  value=z*3
  Value=value*t
  print(value)
}
```

```{r}
Mysecondfn<-function(t,z) { #code is case-sensitive
  value=z*3
  value=value*t
  Print(value)
}
```

```{r}
t=5
z=9
Mysecondfn(t,z)
```

```{r}
t=11
z=8
Mysecondfn(t,z)
```
```{r}
t=100
z=10
Mysecondfn(t,z)
```

# LOOPS

A loop is a collection of commands that are run over and over again. A for loop runs the code a fixed number of times, or on a fixed set of objects. A while loop runs the code until a condition is met.

Sytax for loop: for(name in vector) {commands}

```{r}
for(z in 1:12){print(z)}
```

```{r}
f3<-function(x,y) {
  z1<-x+y
  z2<-x+2*y
  list(result1=z1,result2=z2)
}
```

```{r}
f3(2,5)
```

```{r}
f3<-function(x,y) {
  Z1<-x+y
  z2<-x+2*y
  list(result1=z1,result2=z2)
}
```

```{r}
total<-0
for(i in 1:5) {
  total=total+i
}
total
```

```{r}
total<-0
for(i in 1:10) {
  total=total+i
}
total
```

Syntax for loop: while(condition) {commands}

```{r}
x<-0
while(x<10) {x<-x+4
print(x)}
```

## Exercise
```{r}
total<-0  #Example code
for(i in 1:5) {
  total=total+i
}
print(total)
```

```{r}
total<-0
for(i in 1:20) {
  total=total+(i+1)
}
total
```

```{r}
total<-0
for(i in -10:15) {
  total=total+i
}
total
```

```{r}
total<-0
for(i in -10:10) {
  total=total+exp((i)**(1/i))
}
total
```

```{r}
total<-0
for(i in 0:8) {
  total=3*i
  total1=total+3*i
  print(total)
}
```

```{r}
total<-0
for(i in 0:20) {
  total=total+(1/(2**i))
}
total
```

## PASTE FUNCTION
The Paste function combines several inputs into a single character string.

```{r}
paste("xyz",1:10)
```

```{r}
paste("xyz",c(2,5,7,"test",4.5))
```

```{r}
paste("xyz",1:10,sep=" ")
```

```{r}
paste("xyz",1:10,sep="/")
```

```{r}
append("xyz",1:10)
```

append command is useful to add elements to the end of a list, while the paste command joins the elements and creates a list.

## IF ELSE STATEMENTS

```{r}
a<-c(1,3,5,6) 
if(a>4) {print("bigger than 4")}
else if(a<=1) {print("less than or equal to 1")}
else {print("between 1 and 4")}
if else(a>4,"bigger than 4","less than or equal to 4")
```

```{r}
a<-c(1,3,5,6)
for(i in a) {
if(i>4) {print("bigger than 4")}
else if(i<=1) {print("less than or equal to 1")}
else {print("between 1 and 4")}
}
```

```{r}
a<-c(1,3,5,6)
for(i in a) {
print(ifelse(i>4,"bigger than 4","less than or equal to 4"))
}
```

```{r}
#A2
total<-0
for(i in 1:5) {
  total=total+i
  print(ifelse(5*i<15,"not required","required"))
}
total
```

```{r}
#A3
sales<-c(100,200,50,70,80,150,90) #1 week sales
for(i in sales) {
  if(i<=80) {print("Average Sales")}
  else if(i>150) {print("Very Good Work")}
  else {print("Good Work")}
}
```

