---
title: "18-08-20"
author: "RUCHIKA LALLA 2048130"
date: "8/18/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# INTRODUCTION TO R MARKDOWN

R Markdown is a very helpful feature of R that allows users to compile their programs, outputs and explanations into one single PDF, Word document or HTML file.

## AIM:
Any basic analysis can be carried out in R once a dataset is imported. Thus the aim of this lab is to import datasets using two different techniques and carrying out some exploratory data analysis.

### Question 1:
Import a dataset saved in a text file into R.

```{r}
library(readr)
test <- read_delim("C:/Users/LENOVO/Desktop/Ruchika/MStat/R Programming/data.txt",delim=",")
test
```

Since the text file is delimited using a comma, we use the read_delim() command to create a data frame using the inputs in R.

### Question 2:
Import a dataset into R using Excel and describe the data.

```{r}
library(readxl)
df<- read_excel("C:/Users/LENOVO/Desktop/Ruchika/MStat/R Programming/data.xlsx")
```

The read_excel() command is a useful way of importing Excel datasets into R and using them for further analysis.

```{r}
dim(df)
```

The dim() command gives you the dimensions of the dataset you have selected, i.e. there are 185 rows and 17 columns in the dataset.

```{r}
colnames(df)
```

The colnames() command gives the column headings in the dataset, providing a brief overview of the type of data contained in the analysis.

```{r}
head(df,10)
```

The head() command gives the first 10 entries in the dataset.

```{r}
tail(df,10)
```

The tail() command gives the last 10 entries in the dataset.

```{r}
summary(df)
```
Using summary(), we are able to obtain the summary statistics for each of the variables present in the dataset.

```{r}
library(skimr)
```

skimr is another package that can be used for basic data exploration. Another example is DataExplorer.

```{r}
skim(df)
```

skim() is another way of obtaining summary statistics for the dataset. It also provides inline histograms that provide greater in-depth analysis.

###Question 3:
Create a histogram for any variable in the dataset.

```{r}
hist(df$Sleep)
```

Thus, we are able to plot a histogram for the number of hours of sleep the people in the dataset get on an average.

# CONCLUSION
Thus, we are able to import datasets into R and carry out some basic exploratory analysis.


