---
title: "29-7-20"
author: "RUCHIKA LALLA 2048130"
date: "7/29/2020"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, cache = F}
knitr::opts_chunk$set(error = TRUE)
```

# AIM:
In today's class, we will examine how to use R as a calculator.

For calculations, it is important to remember that R follows BODMAS rule.

# QUESTION 1:
Use 5 arithmetic operations in a single equation.

```{r}
2**(3+((9/4)-(18/7))*(17%/%12))-31*16
```

```{r}
(44%/%12)-(4**6)+(18/7)*(19%%3)
```

# QUESTION 2:
Print 5 string commands.

```{r}
str1="Welcome"
print(str1)
```

```{r}
str2="to"
print(str2)
```

```{r}
str3="this"
print(str3)
```

```{r}
str4="R-Programming"
print(str4)
```

```{r}
str5="class"
print(str5)
```

```{r}
str1="My"
print(str1)
```

```{r}
str2="name"
print(str2)
```

```{r}
str3="is"
print(str3)
```

```{r}
str4="Prakhar"
print(str4)
```

```{r}
str5="Srivastava"
print(str5)
```

# ASSIGN VALUES TO OBJECTS
Name of object is case-sensitive.

```{r}
x<-c(1,2,3)
x
```

```{r}
X
```
Thus, we obtain the error as name of the object is case-sensitive, hence 'x' exists and 'X' does not.

It gives an error because 'X' is not defined.

```{r}
y<-c(4,5,6)
y
```

```{r}
Y
```

```{r}
assign("z",c(7,8,9))
z
```

```{r}
Z
```
Even when using the assign function, it is clear that R is case-sensitive.

# FUNCTIONS FOR OBJECTS
List of objects.

```{r}
ls()<-"x","y","z"
objects()
```
We get an error here since the list has not been correctly defined.

The definition of R here is not correct.

```{r}
ls<-c("x","y","z")
objects()
```

This function means that the list is properly defined, and the objects() function shows all the objects in this file.

Remove Objects:
```{r}
rm("x")
```
This error shows that x has been properly removed and re-execution confirms its removal.

Vector Calculus Examples:
```{r}
y<-4 5 6
```
This is not possible since it is important to define it properly as a list or concatenate the objects.

```{r}
x=c(y,5,y)
x
```

```{r}
sum(x)
```

```{r}
sqrt(x)
```

```{r}
sqrt(sum(x))
```

Here, we were able to compute the sum of x, and the square roots of its components and its total.

Logical Test:
```{r}
LogicalX<-x<5
LogicalX
```

This function tests whether all the elements in x satisfy the given condition or not.

```{r}
logicalx
```
We received an error in this statement because R is case-sensitive.

# BRACKETS:
()- round brackets are the standard brackets.
[]- box brackets are used if we are dealing with index positions of vectors; eg- 
```{r}
x[1]
```
```{r}
x[100]
```
{}- curled brackets are used for functions and loops.
