---
title: "31-08-20"
author: "RUCHIKA LALLA_2048130"
date: "8/31/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# FACTORS

## Definition:

Factors are those data objects in R which are used to categorize the data and store it as levels. Factors can store both strings and integers, and they are used in data analysis in statistical modelling.

Factors can be ordered or unordered, and it is always better to have factors with labels.

## Code:

```{r}
x<-c("yes","yes","no","no","no","yes","yes","yes")
print(x)
```

```{r}
print(is.factor(x))  #to check if x is a factor
```

```{r}
factor_d<-factor(x)  #convert x into a factor
print(factor_d)
print(is.factor(factor_d))
```

## Questions:

### Q) Construct a factor with different values of marital status.
```{r}
data=c(0,1,2,2,2,2,2,1,1,1,1,1,1,1,1,1,1,1,0,0,0,0,0,0,1,1,1,1,1,1,1,2,2,2,2,2,1,1,1,1,1,1)
print(data)
print(is.factor(data))
```

```{r}
mdata=factor(data,labels=c("Single","Married","Divorced"))
print(mdata)
print(is.factor(mdata))
```

```{r}
table(mdata)
```

### Q) Create a factor based on months of a year and order it accordingly.
```{r}
month=c("March","April","December","January","August","May","February","September","July","October","June","November","December","April","May","June","September","July","March","February","May","May","October")
fmonth=factor(month)
print(is.factor(fmonth))
table(fmonth)
```

```{r}
fmonth1=factor(fmonth,levels=c("January","February","March","April","May","June","July","August","September","October","November","December"))
print(is.factor(fmonth1))
table(fmonth1)
```

### Q) Consider the effect of  different levels of fertilizers on growth of a plant. Also find its mean.
```{r}
eff=c(20,30,40,50,10,20,50,30,40,20,10,10,30,40,50,30)
eff=factor(eff,levels =c(10,20,30,40,50),ordered=TRUE)
print(is.factor(eff))
table(eff)
```

```{r}
print(eff)
mean(eff)
```

```{r}
mean(as.numeric(levels(eff)[eff])) #as.numeric converts the value to a number
```

## Basic Diganostic Features of R:

Structure is a R command that gives the data type and basic information about it as its output. It is an important diagnostic feature of R.
```{r}
str(eff)
```

```{r}
str(mtcars)
```

Another diagnostic feature of R is summary, which generally summarizes the data and its key statistical features.
```{r}
summary(eff)
```

```{r}
summary(mtcars)
```

## Accessing Components of a Vector:

```{r}
x<-factor(c("S","M","M","W","D","D","W"))
x[2]   #accessing the 2nd element of the factor
```

```{r}
x[c(1,5)]  #accessing the 1st and 5th elements
```

```{r}
x[-3]  #access all except 3rd element
```

```{r}
x[1]==x[2]
```

```{r}
x[2]!= x[3]
```

```{r}
print(x)
x[c(TRUE,TRUE,FALSE,TRUE)]
```

```{r}
print(eff)
eff[c(TRUE,TRUE,FALSE,TRUE)]
```


```{r}
for (i in x) {
  if (i=="M") {
    print("1")
  }
  else {
    if (i=="S") {
      print("0")
    }
    else {
      print("2")
    }
  }
}
```
